Multi-modality Imagery Database for Plant Phenotyping

### 2015-10-20 datapaper_plants.tex
revision edits

In all cases, seeds were planted in soil covered with a black foam mask in order to minimize the fluorescence background from algal growth.
%
Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection.
Growth conditions as described above were maintained for each set of plants for the duration of image collection.

>>>>

In all cases, seeds were planted in soil covered with a black foam mask in order to minimize the fluorescence background from algal growth.
%
Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before starting the data collection.
Aforementioned growth conditions were maintained for each set of plants for the duration of image collection.

### 2015-10-20 datapaper_prior.tex
revision_Xi
revision edits

The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants.
Thus, non-destructive imaging approaches are taken and the entire plant is imaged.
The LSC database~\cite{scharr2014annotated} is the most relevant one to ours.
It captures a large set of RGB images for Arabidopsis and tobacco plants.
The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant visual appearance.
Our diverse manual labels also enable us to develop algorithms for additional applications such as leaf tracking and leaf alignment.

@@

The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-fluorescent background, it clearly defines the chlorophyll-containing (photosynthetically active) leaf area.
The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
Near infrared (IR) reflectance at $\sim940~nm$ has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
However, it may also be useful in determining leaf angle and curvature~\cite{woolley1971reflectance}.
Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

>>>>

The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants.
Thus, non-destructive imaging approaches are taken and the entire plant is imaged.
The LSC database~\cite{scharr2014annotated} is the most relevant one to ours.
It captures a large set of RGB images for Arabidopsis and tobacco plants.
The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset. 
In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant visual appearance.
Our diverse manual labels also enable us to develop algorithms for additional applications such as leaf tracking and leaf alignment.

@@

The four sensing modalities in MSU-PID provide unique opportunities to comprehensively characterize plant morphological and physiological phenotypes.
The use of chlorophyll fluorescence at $730$ $nm$ to $750$ $nm$ as a tool for evaluating photosynthetic performance is well established~\cite{baker2008chlorophyll}, and against non-fluorescent background, it clearly defines the chlorophyll-containing (photosynthetically active) leaf area.
The depth measurement has been a component of a number of recent non-plant RGB-D databases designed for object recognition~\cite{Lai2011}, scene segmentation~\cite{Silberman2011}, human analysis~\cite{Sung2011,Barbosa:reid12}, and mapping~\cite{sturm12iros}.
By including depth map for a plant database, we anticipate enabling development of new $3$D plant canopy analysis algorithms and thus probing the total energy intake and storage.
Near infrared (IR) reflectance at $\sim$~$940~nm$ has been used by others to detect water content in leaves~\cite{chen2014dissecting}.
However, it may also be useful in determining leaf angle and curvature~\cite{woolley1971reflectance}.
Furthermore, since imaging occurs at a wavelength that is effectively non-absorbing for photosynthesis or known light receptors~\cite{butler1964actton,eskins1992light} in plants, it can be used for imaging during the night cycle to observe night time leaf expansion or in some cases circadian movements~\cite{mcclung2006plant}.

### 2015-10-20 datapapr_labeling.tex
revision edits

\begin{table}[h]
\centering
\caption{Human label performance vs. label propagation performance.
$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
The {\it{SBD}} score is averaged over $3$ plants.}
\begin{tabular}{c|c|c|c|c}
\hline
    & \multicolumn{2}{c|}{fluorescence} & \multicolumn{2}{c}{RGB}\\ \hline
    & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
   day$\_3$ & $0.808$ & $0.804$ & $0.827$ & $0.802$ \\ \hline
   day$\_5$ & $0.830$ & $0.836$ & $0.871$ & $0.837$ \\ \hline
   day$\_9$ & $0.903$ & $0.886$ & $0.877$ & $0.789$ \\ \hline
    average &   $0.847$ & $0.842$ & $0.858$ & $0.809$ \\ \hline
\end{tabular}
\label{tab:labelError}
\end{table}

In the case of the bean sequences, the pixel association between modalities is more difficult as the within-plant depth variations are large.
We found that a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infrared and fluorescence images that use the same camera.

@@

The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
The availability of multiple modalities allows user to design novel experimental setup.
For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent}.

>>>>

\begin{table}[t!]
\centering
\caption{Human label performance vs. label propagation performance.
$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
The {\it{SBD}} score is averaged over $3$ plants.}
\begin{tabular}{c|c|c|c|c}
\hline
    & \multicolumn{2}{c|}{fluorescence} & \multicolumn{2}{c}{RGB}\\ \hline
    & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
   day$\_3$ & $0.808$ & $0.804$ & $0.827$ & $0.802$ \\ \hline
   day$\_5$ & $0.830$ & $0.836$ & $0.871$ & $0.837$ \\ \hline
   day$\_9$ & $0.903$ & $0.886$ & $0.877$ & $0.789$ \\ \hline
    average &   $0.847$ & $0.842$ & $0.858$ & $0.809$ \\ \hline
\end{tabular}
\label{tab:labelError}
\end{table}

In the case of the bean imagery, the pixel association between modalities is more difficult as the within-plant depth variations are large.
We found that a homograph-based mapping performed poorly, and so the manual annotations we supply apply to just the infrared and fluorescence images that use the same camera.

@@

The user may decide to utilize one or multiple modalities of the plant imagery for training and testing respectively.
The availability of multiple modalities allows user to design novel experimental setup.
For example, using RGB and depth modalities for training and RGB for testing can take advantage of additional information during the learning without incurring extra sensor cost during the testing, which can be implemented via either learning with side information~\cite{chen2013boosting}, or transfering learning with missing modality~\cite{ding2014latent,Chen2013b}.
